\chapter{UX Results}
\label{appendix:ux}

\definecolor{agree}{RGB}{0, 122, 0}
\definecolor{disagree}{RGB}{122, 0, 0}
\definecolor{niceButWontCol}{RGB}{222, 222, 0}
\definecolor{toughCol}{RGB}{222, 100, 0}
\definecolor{fixableCol}{cmyk}{0, 0.208, 0.0429, 0.1412}

\newcommand{\tab}{\vspace{0.5cm}}
\newcommand{\username}[1]{\textsc{\textbf{#1}}}
\newcommand{\user}[1]{\item[\username{#1}] \hfill}
\newcommand{\agrees}[1]{\color{agree}\username{#1}\color{black}}
\newcommand{\disagrees}[1]{\color{disagree}\username{#1}\color{black}}
\newcommand{\fixable}[1]{\colorbox{fixableCol}{#1}}
\newcommand{\tough}[1]{\colorbox{toughCol}{#1}}
\newcommand{\cant}[1]{\colorbox{niceButWontCol}{#1}}

\small
\begin{center}
	\fixable{fixable easy (1-2 hrs)} \tough{necessary but tough (\textgreater 10 hrs)} \cant{nice but cant}
\end{center}
\begin{itemize}
	\item {You have just installed the app. You open it for the first time.
		\begin{itemize}
			\item What do you see?
					\begin{itemize}
						\item List of products \agrees{1}, \agrees{2} - ads, \agrees{4}, \agrees{5}
						\item \fixable{Expected the products in reverse chronological order} \agrees{4}
						\item Gray boxes. \agrees{3}
						\item Details of products. \agrees{2}, \agrees{5}
						\item Would rather not have a placeholder image for items without an image \agrees{1}, \disagrees{4} 	
						\item Pictures are a bit small. \agrees{5}
						\item Circle buttons on bottom were getting in the way. \agrees{1}, \agrees{2}, \disagrees{3}, \disagrees{5}
						\item \tough{Expected to have a category section} \agrees{2}, \agrees{3}, \agrees{4}				
						\vspace{0.5cm}
						
						\item GIF avatars of people \agrees{1}, \agrees{3}, \agrees{4}
						\item \fixable{Expects clicking on the user avatar on product card to bring up the user profile} \agrees{1}
						\item \fixable{Expected owner's name to be on the product card along with their avatars} \agrees{4}
						\vspace{0.5cm}
						
						\item Can see a nice chat option \agrees{1} 
						\item Borrow / buy is disabled means those options not available for the product \agrees{1} 
						\item Good that can't borrow own things \agrees{1} 
						\item Some items are closed seeing the red tag. \agrees{2}, \agrees{4}, \agrees{5}
						\vspace{0.5cm}
						
						\item Search bar for finding products. \agrees{2}, \agrees{3}
						\item Wasn't sure what the blue person icon meant. \agrees{4}
						\item \cant{Expected to have a tutorial to explain the basic usage} \agrees{4}
					\end{itemize}
			\item What do you want to do now?
				\begin{itemize}
					\item Search for something. \agrees{3}, \agrees{1}
					\item Click on a product. \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}
					\item Add a product. \agrees{1}, \agrees{5}
				\end{itemize}
		\end{itemize}
		}
		\tab
	\item {
		\begin{itemize}
			\item Navigate back to the home page. (steps \& time)
				\begin{itemize}
					\item Everyone started looking about the app and made their way back to the home page. This task was trivial.
					\item Navigation stack messed up in some order. Couldn't reproduce how they did it. \agrees{1}
				\end{itemize} 
			\item Try to find your profile. How else could you find your profile? (steps \& time)
				\begin{itemize}
					\item Everyone found the profiles before this question was asked. It was trivial.
					\item From the icon on home. \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}, \agrees{5}
					\item From the menu on the top left. \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}, \agrees{5}
					\item From one of own products. \agrees{3}
					\item Prefer the icon on home. \agrees{3}, \agrees{5}
					\item Prefer the menu option. \agrees{1}, \agrees{2}
					\vspace{0.5cm}
					
					\item Cannot change avatar. \agrees{1}
					\item Liked the idea of rating. \agrees{1}, \agrees{4}, \agrees{5}
					\item \fixable{Not sure if the comments are about the products, deals or person's own self}. \agrees{1}, \agrees{2}, \agrees{4}
					\item \tough{\tiny{Not sure what the ratings represent, i.e. expected to see granular ratings e.g. timeliness 4, care of product 3 etc}} \agrees{1}, \agrees{2}
					\item Good that can't rate oneself. \agrees{4}, \agrees{5}
					\item Rated someone. \agrees{3}, \agrees{5}
					\item Failed to rate someone. \agrees{1}
				\end{itemize}
		\end{itemize}
		}
		\tab
	\item You want to post this 'x' on the community to sell, but you also don't mind lending it. What do you do? (steps \& time)
		\begin{itemize}
			\item Everyone followed the expected route, filled in the fields and clicked the green tick. Took less than two minutes.
			\item Click on (+) on home page. \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}, \agrees{5}
			\item Likes the use of toggle buttons for sell or lend options. \agrees{5}
			\item Prefer to have types in defined categories. \agrees{3}, \agrees{4}
			\item Relates types to tags. \agrees{4}
			\item Easy to add and see the scrollable picture. \agrees{1}, \agrees{5}
			\vspace{0.5cm}
			\item \tough{\footnotesize{Noticed the lending bug - where things are always put on for sale and lending regardless of options}}
			\item \fixable{Expected a confirmation} \agrees{4}
			\item \fixable{Expected to be taken to the summary page} \agrees{5}
			\item \fixable{Expected the product to be on top of the list} \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}, \agrees{5}
		\end{itemize}
		\tab	
	\item You're looking for a used 'macbook' to buy. How will you find it? (steps \& time)
		\begin{itemize}
			\item Trivial to search for a product on the home page (less than 30 seconds). But not trivial to get out of the search.
			\item \cant{Search doesn't work on types or wrongly spelt names etc}. \agrees{3}, \agrees{4}, \agrees{5}
			\item \fixable{Expected to see a message or suggestions when no results for a search were found} \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}
			\item Liked the cross to clear the search field. \agrees{3}, \agrees{4}, \agrees{5}
		\end{itemize}
		\tab
	\item You've found a 'moto x'. You can use it for your project. How can you borrow it? (steps \& time) What do you think happens next?
		\begin{itemize}
			\item Trivial to borrow an item. Less than 30 seconds.
			\item Click on borrow button if available. \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}, \agrees{5}
			\item If not available to borrow, contact the user via chat. \agrees{3}
			\item Expected to have the options on the product page too. \agrees{2}, \agrees{5}
			\item Buyer gets notified. \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}, \agrees{5}
			\item Item was reserved. \agrees{2}, \agrees{3}, \agrees{4}
			\item Get in touch with the buyer and exchange. Then complete. \agrees{1}, \agrees{3}, \agrees{4}
			\item Complete immediately. \agrees{2}, \agrees{5}
			\item \cant{Products should be considered closed if both parties complete it} \agrees{4}
		\end{itemize}
		\tab
	\item You want to find out more about the item or its seller. How? (steps \& time)
		\begin{itemize}
			\item Trivial. Found within 30 seconds. Comments about own profile applies here too.
			\item Went to product details page, then owner name. \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}, \agrees{5}
			\item \fixable{\footnotesize{Expected the closed items on a product to be marked on a profile page like on the cards}} \agrees{4}, \agrees{5}
		\end{itemize}
		\tab
	\item How do you know if someone responded to the 'x' you posted earlier? Find such responses on the app. (steps \& time)
		\begin{itemize}
			\item The most difficult task here. Took quite a bit of looking around. More than 60 seconds.
			\item Expected to get a notification (didn't always get sent a notification because of Google servers). \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}, \agrees{5}
			\item Found on product details page. \agrees{1}, \agrees{2}, \agrees{4}, \agrees{5}, \disagrees{3}
			\item \tough{Expected to find separate place on profile for notifications about such things} \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}, \agrees{5}
			\item Expected to have a tab on the menu for notifications directly. \agrees{4}, \agrees{5}
		\end{itemize}
		\tab
	\item You want to accept a request. How? What do you think happens when you accept?
		\begin{itemize}
			\item Trivial and took less than 30 seconds.
			\item Click on accept button on an offer. \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}, \agrees{5}
			\item The other side gets notified. \agrees{1}, \agrees{2}, \agrees{3}, \agrees{4}, \agrees{5}
		\end{itemize}
		\tab
	\item You want to decline a request. How? What do you think happens when you decline a request?
		\begin{itemize}
			\item Trivial. Similar to above.
		\end{itemize} 
		\tab 
		
	\item Note 2 points that could be 'improved' in the app.
		\begin{itemize}
			\item Add meaning to rating \agrees{1}
			\item Improve the interaction with a failed search and make clearing a search better \agrees{1}
			\vspace{0.5cm}
			\item Make notifications clearer to find. \agrees{2}, \agrees{3}, \agrees{5}
			\item Make scrolling better. \agrees{2}
			\vspace{0.5cm}
			\item Add categories for products. \agrees{3}
			\item Separate tab in the menu for own products \agrees{5}
			\vspace{0.5cm}
			\item \fixable{Add time tag to comments}
			\item Order of products in reverse chronological order.
		\end{itemize}
		\tab 
	\item Note 2 points that the app does well.
		\begin{itemize}
			\item Product card layout is clean with three buttons for obvious actions. \agrees{1}, \agrees{3}
			\item Intuitive and clean interface. \agrees{2}, \agrees{4}, \agrees{5}
			\item Animations, loading, fluidity adds life to the app. \agrees{4}
			\item Adding pictures of products is easy, necessary and done well. \agrees{1}
		\end{itemize}		 
\end{itemize}