\chapter{Interview Scripts}
\label{appendix:interview}
\section{Interview 1}
\label{sec:interview1}
\begin{itemize}
	\item What items do you own, but not use often (Once a week or less)?
	\item Which of these items would you share with others?
	\item Why those items and not the others? (If none, then why?)
	\item If another student were to borrow your item, which items - 
		\begin{itemize}
			\item Would you have them pay for i.e. sell? Why?
			\item Would you have them put a deposit for? Why?
			\item Would you make them share an item of their own for i.e. swap? Why?
			\item Would you let them borrow regardless? Why?
			\item Anything else you have to add?
		\end{itemize}
	\item How much does trusting the borrower or lender get in these decisions?
	\item Tell me how you would increase trust in the community to share your belongings?
	\item How can the borrower increase the trust?
	\item How can the lender increase the trust?
	\item How would you go about \& carry out the transaction? How would set up how and where to meet or post?
	\item What would you expect to see in as you open the application? 
	\item What would you want to do first after you open it? 
	\item What other functions would you perform as a user? As a borrower ? As a sharer? 
	\item Which of these features are more important to you and in what order and why such order? 
	\item How would you perform the top 3 features that you have selected? (Ask them to draw out a flowchart like steps for the functions) 
\end{itemize}

\section{Interview 2}
\label{sec:interview2}
\begin{itemize}
	\item {You have just installed the app. You open it for the first time.
		\begin{itemize}
			\item What do you see?
			\item What do you want to do now?
		\end{itemize}
		}
	\item {
		\begin{itemize}
			\item Navigate back to the home page. (steps \& time)
			\item Try to find your profile. How else could you find your profile? (steps \& time)
		\end{itemize}
		}
	\item You want to post this 'x' on the community to sell, but you also don't mind lending it. What do you do? (steps \& time)
	\item You're looking for a used 'macbook' to buy. How will you find it? (steps \& time)
	\item You've found a 'moto x'. You can use it for your project. How can you borrow it? (steps \& time) What do you think happens next?
	\item You want to find out more about the item or its seller. How? (steps \& time)
	\item How do you know if someone responded to the 'x' you posted earlier? Find such responses on the app. (steps \& time)
	\item You want to accept a request. How? What do you think happens when you accept?
	\item You want to decline a request. How? What do you think happens when you decline a request?
	\item Note 2 points that could be 'improved' in the app.
	\item Note 2 points that the app does well. 
\end{itemize}